Elders stove grades and usage summary

### 2020-03-12 indoor_temp_rh_summary.Rmd
plot and summary updates

---
title: "Elders indoor temp/RH summary"
author: "Ethan Walker"
date: "Started 5 March 2020, Updated 5 March 2020"
output: pdf_document
---

@@

```{r}
# Load data
indoor_temp_rh_clean <- read_rds("Output/elders_temp_rh_clean.rds")
elders_ids_linked <- read_rds("Output/elders_ids_linked.rds")
elders_pm <- read_rds("Output/elders_pm_clean.rds")
```

# Summary stats
```{r}
temp_rh_summary <- indoor_temp_rh_clean %>%
  filter(winter_id == 1) %>% 
  group_by(area) %>% 
  summarize_if(is.numeric, list(mean = mean, sd = sd, min = min, 
                                med = median, max = max), na.rm = TRUE) %>% 
  select(-area) %>% 
  t() 
kable(temp_rh_summary, col.names = c("Navajo", "Nez Perce"), 
      digits = 1, align = "c")

@@

```{r, fig.height=6, fig.width=5}
# Boxplot function
boxplots_temp_rh_function <- function(data, variable){

boxplots_temp_rh <- data %>% 
  filter(winter_id == 1) %>% 
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  na.exclude() %>% 
  ggplot(aes(area, plot_var)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_temp_rh

}
```

## Current indoor humidity (%)
```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "rh_indoor_current")
```

## Max indoor humidity (%)
```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "rh_indoor_max")
```

## Min indoor humidity (%)
```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "rh_indoor_min")
```

## Current indoor temperature (C)
```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "temp_indoor_current")
```

## Max indoor temperature (C)
```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "temp_indoor_max")
```

## Min indoor temperature (C)
```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "temp_indoor_min")
```

#### Abstract/manuscript tables ####

# Filter for homes that have PM data
```{r}
# 93 Winter 1 placebo homes have PM data
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home) %>% 
  ungroup() %>% 
  arrange(area, home)

temp_rh_filtered <- indoor_temp_rh_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>% 
  arrange(area, home)
```

# Summarize home data
```{r}
# Summarize numeric vars
kids_temp_rh <- temp_rh_filtered %>%  
  distinct(home, .keep_all = TRUE) %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(rh_indoor_min, na.rm = TRUE), 
            "SD" = sd(rh_indoor_min, na.rm = TRUE),
            "min" = min(rh_indoor_min, na.rm = TRUE), 
            "med" = median(rh_indoor_min, na.rm = TRUE), 
            "max" = max(rh_indoor_min, na.rm = TRUE))
kable(kids_temp_rh, digits = 1, align = "c")

```

>>>>

---
title: "Elders indoor temp/RH summary"
author: "Ethan Walker"
date: "Started 5 March 2020, Updated 12 March 2020"
output: pdf_document
---

@@

```{r}
# Load data
indoor_temp_rh_clean <- read_rds("Output/elders_temp_rh_clean.rds")
elders_ids_linked <- read_rds("Output/elders_ids_linked.rds")
```

```{r, include=FALSE}
# Summary stats

temp_rh_summary <- indoor_temp_rh_clean %>%
  filter(winter_id == 1) %>% 
  group_by(area) %>% 
  summarize_if(is.numeric, list(mean = mean, sd = sd, min = min, 
                                med = median, max = max), na.rm = TRUE) %>% 
  select(-area) %>% 
  t() 
kable(temp_rh_summary, col.names = c("Navajo", "Nez Perce"), 
      digits = 1, align = "c")

@@

```{r}
temp_rh_summary_function <- function(data, var, title_label, y_label) {

  temp_rh_summary <- data %>% 
    filter(winter_id == 1) %>% 
    #select(var) %>% 
    select(area, var) %>% 
    group_by(area) %>% 
    summarize_all(list(mean=mean, sd=sd, min=min, med=median, max=max), na.rm = TRUE)
  temp_rh_summary <<- temp_rh_summary

  temp_rh_summary_plot <- data %>% 
    filter(winter_id == 1) %>% 
    select(area, var) %>% 
    rename(plot_var = var) %>% 
    filter(!is.na(plot_var)) %>% 
    ggplot(aes(area, plot_var)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red",
                 position=position_nudge(x = -0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=mean, geom="text", 
                 size=7, position=position_nudge(x = -0.35, y = 0)) +
    stat_summary(fun.y=median, geom="point", shape=16, size=4, color="blue",
                 position=position_nudge(x = 0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=median, geom="text", 
                 size=7, position=position_nudge(x = 0.35, y = 0)) +
    theme_minimal() +
    labs(title = title_label, subtitle = "Mean = Red, Median = Blue") +
    ylab(y_label) +
    theme(title = element_text(size = 20, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) 
  temp_rh_summary_plot

}

temp_rh_summary_function(indoor_temp_rh_clean, "temp_indoor_current", "Current indoor temp", "degrees C")
temp_rh_summary_function(indoor_temp_rh_clean, "temp_indoor_min", "Min indoor temp", "degrees C")
temp_rh_summary_function(indoor_temp_rh_clean, "temp_indoor_max", "Max indoor temp", "degrees C")
temp_rh_summary_function(indoor_temp_rh_clean, "rh_indoor_current", "Current indoor RH", "%")
temp_rh_summary_function(indoor_temp_rh_clean, "rh_indoor_min", "Min indoor RH", "%")
temp_rh_summary_function(indoor_temp_rh_clean, "rh_indoor_max", "Max indoor RH", "%")
```

### 2020-03-12 medvisit_summary.Rmd
plot and summary updates

---
title: "EldersAIR Med Visit Summary"
author: "Ethan Walker"
date: "Started 11 March 2020, Updated 11 March 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

# Summary stats 
```{r}
medvisit_summary_function <- function(data, var, title_label, y_label) {

@@

  medvisit_plot <- data %>% 
    filter(winter_id == 1) %>% 
    select(area, var) %>% 
    rename(plot_var = var) %>% 
    filter(!is.na(plot_var)) %>% 
    ggplot(aes(area, plot_var)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red",
                 position=position_nudge(x = -0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=mean, geom="text", 
                 size=7, position=position_nudge(x = -0.3, y = 0)) +
    stat_summary(fun.y=median, geom="point", shape=16, size=4, color="blue",
                 position=position_nudge(x = 0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=median, geom="text", 
                 size=7, position=position_nudge(x = 0.3, y = 0)) +
    theme_minimal() +
    labs(title = title_label, subtitle = "Mean = Red, Median = Blue") +
    ylab(y_label) +
    theme(title = element_text(size = 20, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) 
  medvisit_plot

@@

```{r}
medvisit_summary_function <- function(data, var, title_label, y_label) {

>>>>

---
title: "EldersAIR Med Visit Summary"
author: "Ethan Walker"
date: "Started 11 March 2020, Updated 12 March 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

# Cardiovascular outcomes from Med visit
```{r}
medvisit_plot <- elders_medvisit %>% 
  filter(winter_id == 1) %>% 
  select(area, sp02, pr, bp_sys, bp_dia, hr, age, height_inches,
         weight_lbs, bmi) %>% 
  pivot_longer(cols = c("sp02":"bmi"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  ggplot(aes(area, value)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +theme_minimal() +
    theme(strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free_y")
medvisit_plot
```

```{r}
# Cardio plot function

medvisit_summary_function <- function(data, var, title_label, y_label) {

@@

  medvisit_plot <- data %>% 
    filter(winter_id == 1) %>% 
    select(area, var) %>% 
    rename(plot_var = var) %>% 
    filter(!is.na(plot_var)) %>% 
    ggplot(aes(area, plot_var)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red",
                 position=position_nudge(x = -0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=mean, geom="text", 
                 size=7, position=position_nudge(x = -0.35, y = 0)) +
    stat_summary(fun.y=median, geom="point", shape=16, size=4, color="blue",
                 position=position_nudge(x = 0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=median, geom="text", 
                 size=7, position=position_nudge(x = 0.35, y = 0)) +
    theme_minimal() +
    labs(title = title_label, subtitle = "Mean = Red, Median = Blue") +
    ylab(y_label) +
    theme(title = element_text(size = 20, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) 
  medvisit_plot

@@

# Spirometry outcomes from Med visit
## Using only observations when spiro session graded as "acceptable"
```{r}
medvisit_plot <- elders_medvisit %>% 
  filter(winter_id == 1) %>% 
  filter(spiro_status == "Acceptable") %>% 
  select(area, fvc, fev1, fev1_fvc_ratio, fvc_pp, fev1_pp) %>% 
  pivot_longer(cols = c("fvc":"fev1_pp"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  ggplot(aes(area, value)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +theme_minimal() +
    theme(strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free_y")
medvisit_plot
```

```{r}
# Spiro plot function

medvisit_summary_function <- function(data, var, title_label, y_label) {

### 2020-03-12 pm_summary_dustrak.Rmd
plot and summary updates

---
title: "Elders PM Summary"
author: "Ethan Walker"
date: "Started 24 Feb 2020, Updated 10 March 2020"
output: pdf_document
---

@@

pm_by_day <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  mutate(sampling_month = month(pm_datetime_new, abbr = TRUE)) %>% 
  mutate(day_of_week = factor(day_of_week,
                                 levels = c("Monday", "Tuesday", "Wednesday", "Thursday",
                                            "Friday", "Saturday", "Sunday"),
                                 labels = c("Mon", "Tues", "Wed", "Thur", "Fri", "Sat", "Sun"))) %>% 
  #filter(pm < 500) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(sampling_month) %>% 
  summarize("Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25, na.rm = TRUE),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE))
pm_by_day

summary_stats <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  group_by(area) %>% 
  distinct(home) %>% 
  summarize(n())
summary_stats

summary_stats <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  mutate(mean_threshold_25 = if_else(pm_mean >= 25, 1, 0),
         mean_threshold_25 = as.numeric(mean_threshold_25)) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  summarize(sum(mean_threshold_25)/n())
summary_stats
```

# Boxplots for PM by study area
```{r, fig.height=6, fig.width=5}
boxplots_kids_pm <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(pm < 500) %>% 
  ggplot(aes(area, pm)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(0, 500) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm
```

>>>>

---
title: "Elders PM Summary"
author: "Ethan Walker"
date: "Started 24 Feb 2020, Updated 12 March 2020"
output: pdf_document
---

@@

pm_by_day <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  mutate(day_of_week = factor(day_of_week,
                                 levels = c("Monday", "Tuesday", "Wednesday", "Thursday",
                                            "Friday", "Saturday", "Sunday"),
                                 labels = c("Mon", "Tues", "Wed", "Thur", "Fri", "Sat", "Sun"))) %>% 
  #filter(pm < 500) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(day_of_week) %>% 
  summarize("Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25, na.rm = TRUE),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE))
pm_by_day

pm_by_month <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  mutate(sampling_month = month(pm_datetime_new, abbr = TRUE)) %>%
  #filter(pm < 500) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(sampling_month) %>% 
  summarize("Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25, na.rm = TRUE),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE))
pm_by_month

summary_stats <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  group_by(area) %>% 
  distinct(home) %>% 
  summarize(n())
#summary_stats

summary_stats <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  mutate(mean_threshold_25 = if_else(pm_mean >= 25, 1, 0),
         mean_threshold_25 = as.numeric(mean_threshold_25)) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  summarize(sum(mean_threshold_25)/n())
#summary_stats
```

# Boxplots for PM by study area
```{r}
boxplots_pm <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  ggplot(aes(area, pm)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red",
                 position=position_nudge(x = -0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=mean, geom="text", 
                 size=7, position=position_nudge(x = -0.35, y = 0)) +
    stat_summary(fun.y=median, geom="point", shape=16, size=4, color="blue",
                 position=position_nudge(x = 0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=median, geom="text", 
                 size=7, position=position_nudge(x = 0.35, y = 0)) +
    theme_minimal() +
    #ylim(0, 250) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    labs(title = "Area PM2.5, Winter 1", subtitle = "Mean = Red, Median = Blue") +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_pm

boxplots_pm <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  ggplot(aes(area, log(pm))) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red",
                 position=position_nudge(x = -0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=mean, geom="text", 
                 size=7, position=position_nudge(x = -0.35, y = 0)) +
    stat_summary(fun.y=median, geom="point", shape=16, size=4, color="blue",
                 position=position_nudge(x = 0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=median, geom="text", 
                 size=7, position=position_nudge(x = 0.35, y = 0)) +
    theme_minimal() +
    #ylim(0, 250) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    labs(title = "Area PM2.5 (log transformed), Winter 1",
         subtitle = "Mean = Red, Median = Blue") +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_pm
```

### 2020-03-12 stove_grade_usage_summary.Rmd
plot and summary updates

---
title: "Elders stove grades and usage summary"
author: "Ethan Walker"
date: "Started 5 March 2020, Updated 10 March 2020"
output: pdf_document 
---

@@

############ Use only most recent stove grades for analysis ###############

@@

# Summary of stove grades
```{r}
## Look further into NA values? ##
stove_grade_summary <- stove_grades_clean %>% 
  #filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, home, stove_grade, winter_id) %>% 
  #filter(!is.na(stove_grade)) %>% 
  group_by(area, winter_id, stove_grade) %>% 
  distinct(home) %>% 
  summarize(n()) %>% 
  filter(!is.na(stove_grade))
kable(stove_grade_summary, align = "c")

@@

```{r}
multiple_grades <- stove_grades_clean %>% 
  select(area, home, stove_grade, winter_id) %>% 
  filter(winter_id == 1 | winter_id == 2) %>% 
  filter(!is.na(stove_grade)) %>%
  group_by(home) %>% 
  filter(n() > 1) %>% 
  arrange(home, winter_id)
kable(multiple_grades)
```

# Summary of stove use
```{r}
# Summarize numeric vars
stove_use_summary <- stove_use_clean %>% 
  filter(winter_id == 1) %>% 
  group_by(area) %>% 
  summarize("N" = n(),
            "Mean Cords" = mean(wood_cords, na.rm = TRUE),
            "SD Cords" = sd(wood_cords, na.rm = TRUE),
            "Min Cords" = min(wood_cords, na.rm = TRUE), 
            "Median Cords" = median(wood_cords, na.rm = TRUE), 
            "Max Cords" = max(wood_cords, na.rm = TRUE))
kable(stove_use_summary, digits = 1, align = "c")

## Select specific var to assess individually/group by area
table(stove_use_clean$burn_level, stove_use_clean$area, useNA = "ifany")
table(stove_use_clean$wood_type, stove_use_clean$area, useNA = "ifany")
table(stove_use_clean$wood_type_other, stove_use_clean$area, useNA = "ifany")
```

# Stove use summary plots
```{r}
stove_use_plot_function <- function(data, variable) {

stove_use_plot <- data %>% 
  filter(winter_id == 1) %>% 
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  #na.exclude() %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    labs(title = variable) +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    scale_fill_manual(values = jv_palette)
stove_use_plot

@@

stove_use_plot_function(stove_use_clean, "burn_level")
stove_use_plot_function(stove_use_clean, "wood_type")
```

#### Abstract/manuscript tables ####

# Filter for homes that have PM data
```{r}
# 93 Winter 1 placebo homes have PM data
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home) %>% 
  ungroup() %>% 
  arrange(area, home)

stove_use_filtered <- stove_use_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>% 
  arrange(area, home)

stove_grades_filtered <- stove_grades_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>% 
  arrange(area, home)
```

# Summarize home data
```{r}
# Summarize numeric vars
kids_use <- stove_use_filtered %>%  
  #distinct(home, .keep_all = TRUE) %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(wood_cords, na.rm = TRUE), 
            "SD" = sd(wood_cords, na.rm = TRUE),
            "min" = min(wood_cords, na.rm = TRUE), 
            "med" = median(wood_cords, na.rm = TRUE), 
            "max" = max(wood_cords, na.rm = TRUE))
kable(kids_use, digits = 1, align = "c")

# Summarize factor vars
alaska_use <- stove_use_filtered %>%  
  #distinct(home, .keep_all = TRUE) %>% 
  filter(area == "AK") %>% 
  group_by(wood_collect_method) %>% 
  summarize(n = n(), percent = (n()/10)*100)
  #summarize(n = n(), percent = (n()/60)*100)
alaska_use

navajo_use <- stove_use_filtered %>%  
  #distinct(home, .keep_all = TRUE) %>% 
  filter(area == "NN") %>% 
  group_by(wood_collect_method) %>% 
  summarize(n = n(), percent = (n()/23)*100)
  #summarize(n = n(), percent = (n()/138)*100)
navajo_use

montana_use <- stove_use_filtered %>%  
  #distinct(home, .keep_all = TRUE) %>% 
  filter(area == "WMT") %>% 
  group_by(wood_collect_method) %>% 
  summarize(n = n(), percent = (n()/60)*100)
  #summarize(n = n(), percent = (n()/360)*100)
montana_use

kids_use <- rbind(alaska_use, navajo_use, montana_use)
kable(kids_use)

# stove grade table
stove_grades_filtered <- stove_grades_clean %>% 
  # change to correct joining data of interest
  #left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  arrange(area, home, winter_id) %>% 
  group_by(home) %>% 
  #mutate(stove_grade = if_else(is.na(stove_grade), lead(stove_grade), stove_grade)) %>% 
  #filter(pm_home == "true") %>% 
  #filter(winter_id == 1) %>%
  group_by(home, winter_id) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  #filter(!is.na(stove_grade)) %>% 
  ungroup() %>% 
  filter(!is.na(stove_grade)) %>% 
  arrange(area, home)

>>>>

---
title: "Elders stove grades and usage summary"
author: "Ethan Walker"
date: "Started 5 March 2020, Updated 12 March 2020"
output: pdf_document 
---

@@

@@

```{r}
############ Use only most recent stove grades for analysis ###############

## Look further into NA values? ##
stove_grade_summary <- stove_grades_clean %>% 
  #filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, home, stove_grade, winter_id) %>% 
  #filter(!is.na(stove_grade)) %>% 
  group_by(area, winter_id, stove_grade) %>% 
  distinct(home) %>% 
  summarize(n()) %>% 
  filter(!is.na(stove_grade))
kable(stove_grade_summary, align = "c")

@@

```{r}
multiple_grades <- stove_grades_clean %>% 
  select(area, home, stove_grade, winter_id) %>% 
  filter(winter_id == 1 | winter_id == 2) %>% 
  filter(!is.na(stove_grade)) %>%
  group_by(home) %>% 
  filter(n() > 1) %>% 
  arrange(home, winter_id)
#kable(multiple_grades)
```

# Summary of stove use
```{r, include=FALSE}
table(stove_use_clean$wood_type, stove_use_clean$area, useNA = "ifany")
table(stove_use_clean$wood_type_other, stove_use_clean$area, useNA = "ifany")
```

# Stove use summary plots
```{r}
stove_use_plot_function <- function(data, variable, title_label, y_label) {

stove_use_plot <- data %>% 
  filter(winter_id == 1) %>% 
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  filter(!is.na(plot_var)) %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    labs(title = variable) +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    labs(title = title_label) +
    ylab(y_label) +
    scale_fill_manual(values = jv_palette)
stove_use_plot

@@

stove_use_plot_function(stove_use_clean, "burn_level", "Burn level", "count")
stove_use_plot_function(stove_use_clean, "wood_type", "Wood type", "count")
stove_use_plot_function(stove_grades_clean, "stove_grade", "Stove grade", "count")
```

```{r, include=FALSE}
# stove grade tables
stove_grades_filtered <- stove_grades_clean %>% 
  arrange(area, home, winter_id) %>% 
  group_by(home) %>% 
  #mutate(stove_grade = if_else(is.na(stove_grade), lead(stove_grade), stove_grade)) %>% 
  #filter(winter_id == 1) %>%
  group_by(home, winter_id) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  #filter(!is.na(stove_grade)) %>% 
  ungroup() %>% 
  filter(!is.na(stove_grade)) %>% 
  arrange(area, home)
